``Don't tell me what it is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics

### 2015-04-17 manuscript.tex
Updates from ShareLaTeX

 \documentclass[conference]{IEEEtran}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{epstopdf}
\usepackage{subfig}
\usepackage{times}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{graphicx}
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{multicol}
\bstctlcite{IEEEexample:BSTcontrol}
\usepackage[table]{xcolor}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.9}
\usepackage{picture}
\newcommand{\kw}[1]{\textit{#1}}
\newcommand{\quart}[4]{\begin{picture}(75,6)
  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\usepackage{amsmath}
\usepackage{balance}
\usepackage{flushend}
\usepackage{times}
\usepackage{cite}
\usepackage{hyperref}
\hypersetup{
  colorlinks = false,
  hidelinks = true
}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

% New Commands
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

@@

\section{Introduction}
\section{Motivating Example}
\section{Background}
\section{Instance Based Learning}

Assessing the quality of solutions to a real-world problem can be extremely hard. In several applications, researchers have models that can emulate the problem. Using these models it is possible to examine several scenarios in a short period of time, and this can be done in a reproducible manner. However, models aren't always the solution, as we shall see.

There exist several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner, or generation of reliable models take prohibitively long. Software defect prediction is an excellent example of such a case. Models that incorporate all the intricate issues that may lead defects in a product is extremely hard to come by. Moreover, it has been shown that models for different regions within the same data can have very different properties \cite{localvsglobal}.

In this paper we propose the use of an instance based approach in place of the conventional model based approach. Instead of generating solutions and going back to a model to see if the solution has any value, we

@@

@@

To validate the treatments that have been suggested by our planner, we need to have defect predictors that capable of identifying if a certain module may (or may not) have a defect. A recent IEEE TSE paper by Lessmann et al.~\cite{lessmann} compared 21 different leaners for software defect prediction: 
\bi
\item
{\em Statistical classifiers:}
Linear    discriminant analysis,
Quadratic discriminant analysis,
Logistic regression,
Naive Bayes,
Bayesian networks,
Least-angle regression,
Relevance vector machine,

@@

@@

\begin{figure}[tbp!]
  \subfloat[][\label{oracle}]{\includegraphics[width=\linewidth]{./_figs/Oracle}}\\
  \subfloat[][\label{what}]{\includegraphics[width=\linewidth]{./_figs/WHAT}}
  \caption{(a) The defect prediction oracle, (b) The Planning scheme}
  \label{fig:rig}
\end{figure}

@@

The performance prediction data set was obtained from~\cite{}. The data set contains six examples of real world configurable systems: \kw{Apache}, \kw{LLVM}, \kw{x264}, \kw{Berkeley DB (written in C and Java}, and \kw{SQLite}. The systems have different characteristics, different implementation languages, and different configuration mechanisms. The data set is a collection of all possible configurations (with SQLITE being a exception with only 4653 configurations). We perforMedian a 5-fold cross validation study on this data set.

@@

The research conducted by Shepperd and MacDonell~\cite{}, Kampenes~\cite{} and Kocaguenli et al.~\cite{}, highlighted that an ``effect size'' in lieu of a mere hypothesis test is required in order to verfiy if two populations are ``significantly'' different. An ICSE'11 paper by Arcuri~\cite{} endorsed the use of Vargha and Delaney's A12 effect size for reporting results in software engineering. Thus, for hypothesis testing H in Skott-Knott, we use the A12 test and a non-parametric bootstrap sampling~\cite{}.

\section{Experimental Results}
\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{_figs/Histogram}
\caption{Caption}
\label{fig:bugs}
\end{figure}

\begin{figure*}[!t]

\noindent\begin{minipage}{0.5\textwidth}
  {\scriptsize \textbf{Ant}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
      \arrayrulecolor{darkgray}
      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
      1 &     Base &    0.13  &  0.03 & \quart{0}{1}{1}{48}\\
      \hline  2 & 0.25, weighting,  iP=50\% &    0.2  &  0.05 & \quart{3}{3}{4}{48}\\
      \hline  3 & 0.5, weighting,  iP=50\% &    0.26  &  0.06 & \quart{6}{3}{8}{48}\\
      \hline  4 &     0.25 &    0.3  &  0.1 & \quart{7}{6}{10}{48}\\
      4 &   0.25&    0.3  &  0.08 & \quart{8}{4}{10}{48}\\
      \hline  5 & 0.75, weighting,  iP=50\% &    0.42  &  0.13 & \quart{13}{7}{17}{48}\\
      5 &      0.5 &    0.43  &  0.1 & \quart{14}{6}{17}{48}\\
      5 &    0.5&    0.43  &  0.1 & \quart{15}{5}{17}{48}\\
      \hline  6 &   0.75&    0.64  &  0.19 & \quart{22}{10}{29}{48}\\
      6 &     0.75 &    0.63  &  0.08 & \quart{26}{4}{28}{48}\\
      \hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Camel}\\}
{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   Base &    0.15  &  0.05 & \quart{0}{4}{1}{75}\\
\hline  2 &   0.25 &    0.18  &  0.06 & \quart{1}{5}{4}{75}\\
  2 & 0.25&    0.2  &  0.06 & \quart{2}{5}{6}{75}\\
  2 & 0.25, weighting,  iP=50\% &    0.2  &  0.04 & \quart{4}{3}{6}{75}\\
\hline  3 &  0.5&    0.25  &  0.1 & \quart{6}{9}{10}{75}\\
  3 &    0.5 &    0.26  &  0.12 & \quart{6}{11}{11}{75}\\
  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.11 & \quart{10}{9}{13}{75}\\
\hline  4 & 0.75&    0.39  &  0.16 & \quart{19}{13}{22}{75}\\
  4 &   0.75 &    0.42  &  0.17 & \quart{15}{15}{25}{75}\\
  4 & 0.75, weighting,  iP=50\% &    0.42  &  0.1 & \quart{20}{9}{25}{75}\\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & 0.25, weighting,  iP=50\% &    0.15  &  0.04 & \quart{0}{2}{0}{55}\\
\hline  2 &     Base &    0.16  &  0.0 & \quart{1}{0}{1}{55}\\
  2 &     0.25 &    0.18  &  0.06 & \quart{1}{4}{2}{55}\\
  2 &   0.25&    0.2  &  0.06 & \quart{1}{4}{3}{55}\\
\hline  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.08 & \quart{7}{5}{9}{55}\\
\hline  4 &      0.5 &    0.33  &  0.11 & \quart{8}{7}{12}{55}\\
  4 &    0.5&    0.37  &  0.09 & \quart{10}{6}{14}{55}\\
\hline  5 & 0.75, weighting,  iP=50\% &    0.38  &  0.16 & \quart{12}{10}{15}{55}\\
\hline  6 &   0.75&    0.56  &  0.08 & \quart{25}{5}{27}{55}\\
  6 &     0.75 &    0.57  &  0.12 & \quart{25}{7}{27}{55}\\[-0.01cm]
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Jedit}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   Base &    0.06  &  0.01 & \quart{0}{0}{0}{64}\\
\hline  2 & 0.25&    0.08  &  0.06 & \quart{0}{4}{1}{64}\\
  2 &   0.25 &    0.09  &  0.05 & \quart{0}{3}{2}{64}\\
\hline  3 & 0.25, weighting,  iP=50\% &    0.12  &  0.08 & \quart{1}{5}{4}{64}\\
\hline  4 &  0.5&    0.16  &  0.09 & \quart{4}{6}{6}{64}\\
  4 &    0.5 &    0.17  &  0.09 & \quart{4}{6}{7}{64}\\
\hline  5 & 0.5, weighting,  iP=50\% &    0.22  &  0.11 & \quart{8}{8}{10}{64}\\
  5 & 0.75&    0.26  &  0.18 & \quart{9}{12}{13}{64}\\
\hline  6 &   0.75 &    0.38  &  0.31 & \quart{11}{21}{21}{64}\\
  6 & 0.75, weighting,  iP=50\% &    0.41  &  0.17 & \quart{17}{12}{24}{64}\\
\hline \end{tabular}}
\end{minipage}

>>>>

 \documentclass[conference]{IEEEtran}
\usepackage{subfig}
\usepackage{wrapfig}
 \usepackage{amsmath}
 \usepackage{url}
 \usepackage{pifont}
\usepackage{rotating}
%\usepackage{balance} 
\usepackage{color, colortbl}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage{program}
\usepackage{cite}
\usepackage{alltt}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\textsection\ref{sec:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\definecolor{lightgray}{gray}{0.975}
\usepackage{fancyvrb}
\usepackage{stfloats}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amsmath} 
\DeclareMathOperator*{\argmin}{arg\,min} 
\DeclareMathOperator*{\argmax}{arg\,max}

\definecolor{darkgreen}{rgb}{0,0.3,0}

\usepackage[table]{xcolor}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\newcommand{\G}{\cellcolor{green}}
\newcommand{\Y}{\cellcolor{yellow}}

\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
\newenvironment{changed}{\par\color{MyDarkBlue}}{\par}

\newcommand{\ADD}[1]{\textcolor{MyDarkBlue}{{\bf #1}}}
\newcommand{\addit}[1]{\begin{changed}\input{#1}\end{changed}}

\usepackage{color}
\usepackage{listings}
\usepackage{setspace}

\definecolor{Gray}{gray}{0.9}
\newcommand{\kw}[1]{\textit{#1}}
\newcommand{\quart}[4]{\begin{picture}(75,6)
  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
% New Commands

\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{0,0,1}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{1,1,1}

\lstnewenvironment{python}[1][]{
\lstset{
mathescape,
numbers=#1,
numberstyle=\footnotesize,
numbersep=0.5em,
xleftmargin=0em,
framextopmargin=2em,
framexbottommargin=2em,
showspaces=false,
showtabs=false,
showstringspaces=false,
tabsize=2,
% Basic
basicstyle=\ttfamily\small\setstretch{0.8},
backgroundcolor=\color{Background},
language=Python,
% Comments
commentstyle=\color{Comments}\slshape,
% Strings
stringstyle=\color{Strings},
morecomment=[s][\color{Strings}]{"""}{"""},
morecomment=[s][\color{Strings}]{'''}{'''},
% keywords
morekeywords={[1]import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert, dot, norm, zip, sorted},
keywordstyle={[1]\color{Code}\bfseries},
% additional keywords
morekeywords={[3]fastmap, project, furthest, split, where,clusterer, getExemplar, projection, mutate, WHAT, knn},
keywordstyle={[3]\color{Keywords}\bfseries},
morekeywords={[2]@invariant},
keywordstyle={[2]\color{Decorators}\slshape},
emph={self},
emphstyle={\color{self}\slshape},
%
}}{}

@@

\section{Introduction}
{\bf RQ1: Can Instance-based Learning techniques be used to create Planning tools that can better analyse software defect?}

{\bf RQ2: Can lessons learnt from local search operators be useful for generating solutions that can be used to mitigate defects in software systems?}

{\bf RQ3: Can such instance-based planners be applied to other software engineering paradigms?}
We check if the proposed instance-based planner is applicable to performance prediction.

\section{Motivating Example}
\section{Background}
\section{Instance Based Learning}

Assessing the quality of solutions to a real-world problem can be extremely hard~\cite{menzies2005xomo}. In several software engineering applications, researchers have models that can emulate the problem, for instance there is the COCOMO effort model~\cite[p29-57]{boehm2009software}, the COQUALMO defect model~\cite[p254-268]{boehm2009software}, Madachy’s schedule risk model~\cite[p284-291]{boehm2009software}, to name a few. Using these models it is possible to examine several scenarios in a short period of time, and this can be done in a reproducible manner. However, models aren't always the solution, as we shall see.

There exist several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner, or generation of reliable models take prohibitively long ~\cite{Ludewig2003}. Software defect prediction is an excellent example of such a case. Models that incorporate all the intricate issues that may lead defects in a product is extremely hard to come by. Moreover, it has been shown that models for different regions within the same data can have very different properties \cite{localvsglobal}. This makes it extremely hard for one to design planning systems that are capable of mitigating these defects.

In this paper we propose the use of an instance based approach, an example of case based reasoning strategy, in place of the conventional model based approach. Instance based approaches have been used extensively by the effort estimation community, see~\cite{keung2008analogy, 6600685, walkerden1999empirical, shepperd1997estimating, kocaguneli2010use, some more form p1703 line 2}. This approach has been proposed as an alternative to closed form mathematical models of other modeling methods such as regression \cite{keung2008analogy}. There are several other reasons for instance based approaches being a useful tool, see~\cite{6600685}. As pointed out by~\cite{walkerden1999empirical} it can be used with partial knowledge of the target project at an early stage which could be a very useful tool in preventing software defects. Instance based approaches are also rather robust in handling cases with sparse samples \cite{1438374}. All these features are desirable and suggest that instance-based approach is a useful adjunct to traditional model based approach.

We would like to stress that the purpose of our work is not to promote instance-based planning over model based analytics, rather it is to suggest an alternative when model based approaches cannot be used.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{_figs/WHAT-Clusters2.pdf}
\caption{WHAT}
\label{fig:whatflow}
\end{figure}

\begin{figure}[!b]
\begin{python}[right]
def fastmap(data): 
  """Project data on a line 
     between 2 distant points
  """
  z          = random.choose(data)
  east       = furthest(z, data)
  west       = furthest(east, data)
  data.poles = (west,east)
  c          = dist(west,east)     
  for one in data.members: 
    one.pos = project(west,east,c,one)
  data = sorted(data) # sorted by 'pos'
  return split(data)

def project(west, east, c, x): 
  "Project x onto line east to west"
  a = dist(x,west)
  b = dist(x,east)
  return (a*a + c*c - b*b)/(2*c) #cosine rule

def furthest(x,data): 
  # what is furthest from x?
  out, max = x,0
  for y in data:
    d = dist(x,y)
    if d > max: out, max = y, d
  return out

def split(data): # Split at median
   mid = len(data)/2; 
  return data[mid:], data[:mid]

def where(data, scores={}, 
          lvl=10000, prune=True):  
  "Recursively split data into 2 equal sizes."
  if lvl < 1: 
     return data # stop if out of levels
  leafs      = [] # Empty Set
  left,right = fastmap(data)
  west, east = data.poles
  $\omega=\sqrt{\mu}$ # enough data for recursion
  goWest = len(left) > $\omega$  
  goEast = len(right) > $\omega$ 
  if prune: # if not pruning, ignore this step
    if goEast and better(west,east,scores): 
       goEast = False 
    if goWest and better(east,west,scores): 
       goWest = False 
  if goWest:  
     leafs += where(left,  lvl - 1, prune)  
  if goEast:  
     leafs += where(right, lvl - 1, prune) 
  return leafs

\end{python}
\caption{Clustering with WHERE}
\label{fig:fastmapCode}   
\end{figure}

\begin{figure}[!t]
\begin{python}[left]
def clusterer():
 "Create clusters using WHERE"

def getExemplar():
  """
  Identify the contour that exemplifies
  the test Instance the most
  """
  contours = []
  ClusterRows = clusterer()
  while ClusterRows:
    one = ClusterRows.pop()
    two = knn(one, ClusterRows)[1]
    contours.append([one, two])
  return contours

def projection(one, two, three):
  "Compute projection of three on one & two"
  if one.score() > two.score():
    bad, good = one, two
  else:
    bad, good = two, one
  plane = [b - a for a, b in zip(
            bad.rep(), good.rep())]
  Norm = norm(plane)
  unitVect = [p / Norm for p in plane]
  proj = dot(three - bad.rep(), unitVect)
  return proj

def mutate(me, others):
  "Mutate 'me' towards 'others'"
  return [my + ext * (good - my) 
    	 for my, good in zip(me, others)]

def WHAT():
  contours = getExemplar()
  for rows in defectiveRows:
    vtx = sorted(
        contours,
        key=lambda F: projection(
        F[0], F[1], rows), reverse=True)[0]

    [good, bad] = sorted(vtx
            , key=lambda F: F.score())
    newRows.append(mutate(rows, good))
  return newRows
\end{python}
\caption{Instance-based Planning using WHAT}
\label{fig:WHAT}   
\end{figure}

@@

To validate the treatments that have been suggested by our planner, we need to have defect predictors that capable of identifying if a certain module may (or may not) have a defect. A recent IEEE TSE paper by Lessmann et al.~\cite{lessmann} compared 21 different learners for software defect prediction: 
\bi
\item
{\em Statistical classifiers:}
Linear    discriminant analysis,
Quadratic discriminant analysis,
Logistic regression,
Naive Bayes,
Bayesian networks,
Least-angle regression,
Relevance vector machine,

@@

\begin{figure}[!tb]
  \renewcommand{\baselinestretch}{0.8}\begin{center}
{\scriptsize
\begin{tabular}{l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~}}
  \hline
  \rowcolor{lightgray}
  Data & Symbol & Training & Testing & Training Samples& Defective &\% Defective \\\hline

Ant & ant & 1.5, 1.6  &1.7 & 644&124&19.25\\

Camel & cam & 1.2, 1.4 & 1.6 & 1480&361 & 24.39\\

Ivy & ivy & 1.1, 1.4 & 2.0  & 352 & 79 & 22.44\\

Jedit & jed & 4.1, 4.2 & 4.3 & 679 & 127 & 18.70\\

Log4j & log & 1.0, 1.1 & 1.2 & 244 & 71 & 29.09\\

Lucene & luc & 2.0, 2.2 & 2.4 & 442 & 235 & 53.16\\

Poi & poi & 2.0, 2.5 & 3.0 & 699 & 285 & 40.77\\

Synapse & syn & 1.0, 1.1 & 1.2 & 379 & 76 & 20.05\\

Velocity & vel & 1.4, 1.5 & 1.6 & 410& 289 & 70.48\\

Xalan & xal &2.5, 2.6 &2.7 & 1688 & 798 & 47.27\\\hline
\end{tabular}}
\end{center}
\caption{Attributes of the defect datasets}\label{fig:ck}
\end{figure}

@@

\begin{figure}[tbp!]
%   \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{./_figs/Oracle}}\\
  \includegraphics[width=\linewidth]{./_figs/WHAT}
  \caption{The Planning scheme}
  \label{fig:what}
\end{figure}

@@

In order to answer {\bfseries RQ4}, we have used the performance prediction data set was obtained from the PROMISE repository~\cite{}. The data set contains six examples of real world configurable systems: \kw{Apache}, \kw{LLVM}, \kw{x264}, \kw{Berkeley DB (written in C and Java}, and \kw{SQLite}. The systems have different characteristics, different implementation languages, and different configuration mechanisms. The data set is a collection of all possible configurations (with SQLITE being a exception with only 4653 configurations).

@@

The research conducted by Shepperd and MacDonell~\cite{shepperd12a}, Kampenes~\cite{kampenes07} and Kocaguenli et al.~\cite{}, highlighted that an ``effect size'' in lieu of a mere hypothesis test is required in order to verfiy if two populations are ``significantly'' different. An ICSE'11 paper by Arcuri~\cite{} endorsed the use of Vargha and Delaney's A12 effect size for reporting results in software engineering. Thus, for hypothesis testing H in Skott-Knott, we use the A12 test and a non-parametric bootstrap sampling~\cite{}.

\section{Experimental Results}
\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{_figs/histograms.pdf}
\caption{Caption}
\label{fig:bugs}
\end{figure}

\begin{figure*}[htbp!]

\noindent\begin{minipage}{0.5\textwidth}
  {\scriptsize \textbf{Ant}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
      \arrayrulecolor{darkgray}
      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
      1 &     Base &    0.13  &  0.03 & \quart{0}{1}{1}{48}\\
      \hline  2 & 0.25, weighting,  iP=50\% &    0.2  &  0.05 & \quart{3}{3}{4}{48}\\
      \hline  3 & 0.5, weighting,  iP=50\% &    0.26  &  0.06 & \quart{6}{3}{8}{48}\\
      \hline  4 &     0.25 &    0.3  &  0.1 & \quart{7}{6}{10}{48}\\
      4 &   0.25, weighting&    0.3  &  0.08 & \quart{8}{4}{10}{48}\\
      \hline  5 & 0.75, weighting,  iP=50\% &    0.42  &  0.13 & \quart{13}{7}{17}{48}\\
      5 &      0.5 &    0.43  &  0.1 & \quart{14}{6}{17}{48}\\
      5 &    0.5, weighting&    0.43  &  0.1 & \quart{15}{5}{17}{48}\\
      \hline  6 &   0.75, weighting&    0.64  &  0.19 & \quart{22}{10}{29}{48}\\
      6 &     0.75 &    0.63  &  0.08 & \quart{26}{4}{28}{48}\\
      \hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Camel}\\}
{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   Base &    0.15  &  0.05 & \quart{0}{4}{1}{75}\\
\hline  2 &   0.25 &    0.18  &  0.06 & \quart{1}{5}{4}{75}\\
  2 & 0.25, weighting&    0.2  &  0.06 & \quart{2}{5}{6}{75}\\
  2 & 0.25, weighting,  iP=50\% &    0.2  &  0.04 & \quart{4}{3}{6}{75}\\
\hline  3 &  0.5, weighting&    0.25  &  0.1 & \quart{6}{9}{10}{75}\\
  3 &    0.5 &    0.26  &  0.12 & \quart{6}{11}{11}{75}\\
  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.11 & \quart{10}{9}{13}{75}\\
\hline  4 & 0.75, weighting&    0.39  &  0.16 & \quart{19}{13}{22}{75}\\
  4 &   0.75 &    0.42  &  0.17 & \quart{15}{15}{25}{75}\\
  4 & 0.75, weighting,  iP=50\% &    0.42  &  0.1 & \quart{20}{9}{25}{75}\\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & 0.25, weighting,  iP=50\% &    0.15  &  0.04 & \quart{0}{2}{0}{55}\\
\hline  2 &     Base &    0.16  &  0.0 & \quart{1}{0}{1}{55}\\
  2 &     0.25 &    0.18  &  0.06 & \quart{1}{4}{2}{55}\\
  2 &   0.25, weighting&    0.2  &  0.06 & \quart{1}{4}{3}{55}\\
\hline  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.08 & \quart{7}{5}{9}{55}\\
\hline  4 &      0.5 &    0.33  &  0.11 & \quart{8}{7}{12}{55}\\
  4 &    0.5, weighting&    0.37  &  0.09 & \quart{10}{6}{14}{55}\\
\hline  5 & 0.75, weighting,  iP=50\% &    0.38  &  0.16 & \quart{12}{10}{15}{55}\\
\hline  6 &   0.75, weighting&    0.56  &  0.08 & \quart{25}{5}{27}{55}\\
  6 &     0.75 &    0.57  &  0.12 & \quart{25}{7}{27}{55}\\[-0.01cm]
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Jedit}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   Base &    0.06  &  0.01 & \quart{0}{0}{0}{64}\\
\hline  2 & 0.25, weighting&    0.08  &  0.06 & \quart{0}{4}{1}{64}\\
  2 &   0.25 &    0.09  &  0.05 & \quart{0}{3}{2}{64}\\
\hline  3 & 0.25, weighting,  iP=50\% &    0.12  &  0.08 & \quart{1}{5}{4}{64}\\
\hline  4 &  0.5, weighting&    0.16  &  0.09 & \quart{4}{6}{6}{64}\\
  4 &    0.5 &    0.17  &  0.09 & \quart{4}{6}{7}{64}\\
\hline  5 & 0.5, weighting,  iP=50\% &    0.22  &  0.11 & \quart{8}{8}{10}{64}\\
  5 & 0.75, weighting&    0.26  &  0.18 & \quart{9}{12}{13}{64}\\
\hline  6 &   0.75 &    0.38  &  0.31 & \quart{11}{21}{21}{64}\\
  6 & 0.75, weighting,  iP=50\% &    0.41  &  0.17 & \quart{17}{12}{24}{64}\\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Log4j}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   Base &    0.06  &  0.03 & \quart{0}{4}{4}{139}\\
\hline  2 & 0.25, weighting&    0.09  &  0.04 & \quart{4}{6}{8}{139}\\
  2 &   0.25 &    0.09  &  0.06 & \quart{4}{8}{8}{139}\\
  2 & 0.25, weighting,  iP=50\% &    0.09  &  0.04 & \quart{4}{6}{8}{139}\\
  2 &    0.5 &    0.1  &  0.07 & \quart{4}{10}{10}{139}\\
\hline  3 &  0.5, weighting&    0.12  &  0.03 & \quart{10}{4}{12}{139}\\
\hline  4 & 0.75, weighting&    0.13  &  0.11 & \quart{10}{15}{14}{139}\\
  4 &   0.75 &    0.13  &  0.06 & \quart{12}{9}{14}{139}\\
  4 & 0.5, weighting,  iP=50\% &    0.13  &  0.06 & \quart{10}{8}{14}{139}\\
\hline  5 & 0.75, weighting,  iP=50\% &    0.19  &  0.11 & \quart{17}{15}{22}{139}\\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Lucene}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &  0.25 &    0.05  &  0.02 & \quart{1}{4}{3}{188}\\
  1 & 0.25, weighting&    0.05  &  0.04 & \quart{0}{7}{3}{188}\\
\hline  2 &   0.5 &    0.07  &  0.04 & \quart{3}{8}{7}{188}\\
  2 & 0.25, weighting,  iP=50\% &    0.07  &  0.04 & \quart{3}{8}{7}{188}\\
  2 & 0.5, weighting&    0.08  &  0.05 & \quart{5}{10}{9}{188}\\
\hline  3 & 0.5, weighting,  iP=50\% &    0.1  &  0.03 & \quart{9}{6}{13}{188}\\
  3 &  Base &    0.1  &  0.03 & \quart{7}{6}{13}{188}\\
\hline  4 & 0.75, weighting,  iP=50\% &    0.13  &  0.09 & \quart{9}{18}{19}{188}\\
  4 &  0.75 &    0.15  &  0.08 & \quart{13}{16}{23}{188}\\
  4 & 0.75, weighting&    0.15  &  0.11 & \quart{11}{21}{23}{188}\\
\hline \end{tabular}}
\end{minipage}
